Spikes demo

### 2018-08-23 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

```{r plot-simulated-data, fig.height=5, fig.width=10}
par(cex.axis = 1,cex.lab = 1.5)
plot(mu.sp,type = 'l',ylim = c(-0.05,1),xlab = "position",
     ylab = "",lwd = 1.7,xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.sp + 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
lines(mu.sp - 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
points(x.sim,cex = 0.7,pch = 16,col = "darkblue")
```

@@

Get shrunken estimates of the wavelet coefficients.

@@

```{r plot-wc-histogram, fig.height=4, fig.width=6}
par(cex.axis = 1,cex.lab = 1.5)
hist(wc.sim[4,],breaks = 2,xlab = "observed wavelet coefficients",
     xlim = c(-25,25),ylim = c(0,600),col = "darkblue",xaxp = c(-25,25,10),
     yaxp = c(0,600,6),main = "")
hist(wc.sim[10,],breaks = 40,add = TRUE,col = "darkorange")
```

@@

```{r wc-scatterplot, fig.height=5, fig.width=5}
par(cex.axis = 1,cex.lab = 1.5)
plot(c(),c(),xlab = "observed wavelet coefficients",
     ylab = "shrunken wavelet coefficients",
     xlim = c(-2.5,2.5),ylim = c(-2.5,2.5))
abline(0,1,lty = 1,col = "gray",lwd = 1)
points(wc.sim[10,],wc.sim.shrunk[[9]]$PosteriorMean,pch = 20,cex = 1,
       col = "darkorange")
points(wc.sim[4,],wc.sim.shrunk[[3]]$PosteriorMean,pch = 20,cex = 1,
       col = "darkblue")
```

@@

```{r}
wc.sig.3 <- 1/wc.pres[[3]]
p <- ggplot(data.frame(observed = wc.sim[4,],
                       shrunken = wc.sim.shrunk[[3]]$PosteriorMean,
                       se       = wc.sig.3),
            aes(x = observed,y = shrunken,col = se)) +
  geom_point(na.rm = TRUE) +
  xlim(c(-1,1)) +
  ylim(c(-1,1)) +
  scale_color_gradientn(colors = c("deepskyblue","darkblue")) +
  theme_cowplot()
print(p)
```

The scale = 7 WCs are strongly shrunk toward zero, whereas the scale =
1 WCs are not shrunk nearly as much; SMASH infers from the data that
the scale = 7 WCs are heavily concentrated around zero, and
consequently SMASH shrinks them more strongly.

Plot the ground-truth signal (mean function) and the signals
recovered by the TI thresholding and smash methods.

```{r}
par(cex.axis = 0.8)
plot(mu.sp,type = "l",col = "black",lwd = 2,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 1.5)
lines(mu.smash,col = "orangered",lwd = 1.5)
cat("Demo is over.\n")
```

>>>>

```{r plot-simulated-data, fig.height=5, fig.width=10}
par(cex.axis = 1,cex.lab = 1.25)
plot(mu.sp,type = 'l',ylim = c(-0.05,1),xlab = "position",
     ylab = "",lwd = 1.7,xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.sp + 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
lines(mu.sp - 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
points(x.sim,cex = 0.7,pch = 16,col = "darkblue")
```

@@

Get the shrunken estimates of the wavelet coefficients.

@@

```{r plot-wc-histogram, fig.height=4, fig.width=6}
par(cex.axis = 1,cex.lab = 1.25)
hist(wc.sim[4,],breaks = 2,xlab = "observed wavelet coefficients",
     xlim = c(-25,25),ylim = c(0,600),col = "darkblue",xaxp = c(-25,25,10),
     yaxp = c(0,600,6),main = "")
hist(wc.sim[10,],breaks = 40,add = TRUE,col = "darkorange")
```

@@

```{r wc-scatterplot, fig.height=5, fig.width=5}
par(cex.axis = 1,cex.lab = 1.25)
plot(c(),c(),xlab = "observed wavelet coefficients",
     ylab = "shrunken wavelet coefficients",
     xlim = c(-2.5,2.5),ylim = c(-2.5,2.5))
abline(0,1,lty = 1,col = "gray",lwd = 1)
points(wc.sim[10,],wc.sim.shrunk[[9]]$PosteriorMean,pch = 20,cex = 1,
       col = "darkorange")
points(wc.sim[4,],wc.sim.shrunk[[3]]$PosteriorMean,pch = 20,cex = 1,
       col = "darkblue")
```

Observe that the scale = 7 WCs are strongly shrunk toward zero,
whereas the scale = 1 WCs are not shrunk nearly as much; SMASH
infers from the data that the scale = 7 WCs are heavily concentrated
around zero, and consequently SMASH shrinks them more strongly.

@@

```{r wc-scatterplot-2, fig.height=3.75, fig.width=5}
wc.sig.3 <- 1/wc.pres[[3]]
p <- ggplot(data.frame(observed = wc.sim[4,],
                       shrunken = wc.sim.shrunk[[3]]$PosteriorMean,
                       se       = wc.sig.3),
            aes(x = observed,y = shrunken,col = se)) +
  geom_point(na.rm = TRUE) +
  xlim(c(-1,1)) +
  ylim(c(-1,1)) +
  scale_color_gradientn(colors = c("deepskyblue","darkblue")) +
  theme_cowplot()
print(p)
```

From this plot, we see that SMASH shrinks WCs differently
depending on their precision; specifically, WCs that are less
precise---i.e., higher standard error (s.e.)---are shrunk more
strongly toward zero.

Finally, we plot the ground-truth signal (the mean function, drawn as
a black line) and the signals recovered by TI thresholding (light blue
line) and SMASH (the red line). The TI thresholding estimate shows
notable artifacts.

```{r plot-mean-signal-vs-estimates, fig.height=5, fig.width=10}
par(cex.axis = 1)
plot(mu.sp,type = "l",col = "black",lwd = 2,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 2)
lines(mu.smash,col = "orangered",lwd = 2)
```
